Attrition

### 2022-02-18 docs/00_participants.Rmd
Render README as target

attrition <- attrition %>% 
	mutate(
		valid_gaze = valid_gaze_prime & valid_gaze_target,
		valid_status = case_when(
			!valid_vocab ~ "Invalid vocabulary",
			!valid_gaze ~ "Invalid gaze",
			!valid_participant ~ "Invalid participant",
			TRUE ~ "Valid"
		))

>>>>

attrition <- attrition %>% 
	mutate(
		valid_gaze = valid_gaze_prime & valid_gaze_target,
		valid_status = case_when(
			!valid_gaze ~ "Invalid gaze",
			!valid_participant ~ "Invalid participant",
			TRUE ~ "Valid"
		))

### 2022-02-18 docs/02_vocabulary.Rmd
Render README as target

attrition <- attrition %>% 
	mutate(
		valid_gaze = valid_gaze_prime & valid_gaze_target,
		valid_status = case_when(
			!valid_vocab ~ "Invalid vocabulary",
			!valid_gaze ~ "Invalid gaze",
			!valid_participant ~ "Invalid participant",
			TRUE ~ "Valid"
		))

participants <- participants %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(participant) %>% 
	left_join(vocabulary) %>% 
	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1]) %>% 
	filter(location=="Barcelona")
```

@@

```{r vocabulary_l1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
sample_size <- participants %>% 
	filter(
		participant %in% fit_l1_4$data$participant
	) %>% 
	count(age_group, location)

@@

# vocabulary
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	stat_pointinterval(
		aes(lp, vocab_size_l1, group = lp),
		position = position_nudge(x = 0.2),
		.width = c(0.95, 0.89, 0.50),
		point_size = 3
	) +
	geom_point(
		aes(lp, vocab_size_l1, color = lp),
		shape = 1, size = 3, stroke = 1.5, alpha = 0.75,
		position = position_jitter(width = 0.1, seed = 888)
	) +
	geom_text(
		data = sample_size_lp,
		aes(x = 1.5, y = 0, label = paste0("N = ", n), group = lp),
		show.legend = FALSE, position = position_dodge(width = 2)
	) +
	labs(
		y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group",
		title = "L1 vocabulary size",
		subtitle = "Percentage of words in L1 reported to be understood from the vocabulary checklist"
	) +
	guides(colour = "none") +
	scale_color_manual(aesthetics = "slab_color", values = pal_futurama()(2)) +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = "top",
		panel.grid.major.x = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9)
	)

@@

# vocabulary
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	stat_pointinterval(
		aes(lp, vocab_size_total, group = lp),
		position = position_nudge(x = 0.2),
		.width = c(0.95, 0.89, 0.50),
		point_size = 3
	) +
	geom_point(
		aes(lp, vocab_size_total, color = lp),
		shape = 1, size = 3, stroke = 1.5, alpha = 0.75,
		position = position_jitter(width = 0.1, seed = 888)
	) +
	geom_text(
		data = sample_size_lp,
		aes(x = 1.5, y = 0, label = paste0("N = ", n), group = lp),
		show.legend = FALSE, position = position_dodge(width = 2)
	) +
	labs(
		y = "Receptive vocabulary (total)", colour = "Group", fill = "Group",
		title = "Total vocabulary size",
		subtitle = "Percentage of words in L1+L2 reported to be understood from the vocabulary checklist"
	) +
	guides(colour = "none") +
	scale_color_manual(aesthetics = "slab_color", values = pal_futurama()(2)) +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = "top",
		panel.grid.major.x = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9)
	)

@@

# vocabulary
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	stat_pointinterval(
		aes(lp, vocab_size_conceptual, group = lp),
		position = position_nudge(x = 0.2),
		.width = c(0.95, 0.89, 0.50),
		point_size = 3
	) +
	geom_point(
		aes(lp, vocab_size_conceptual, color = lp),
		shape = 1, size = 3, stroke = 1.5, alpha = 0.75,
		position = position_jitter(width = 0.1, seed = 888)
	) +
	geom_text(
		data = sample_size_lp,
		aes(x = 1.5, y = 0, label = paste0("N = ", n), group = lp),
		show.legend = FALSE, position = position_dodge(width = 2)
	) +
	labs(
		y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group",
		title = "Conceptual vocabulary size",
		subtitle = "Percentage of lexicalised concepts reported to be understood from the vocabulary checklist"
	) +
	guides(colour = "none") +
	scale_color_manual(aesthetics = "slab_color", values = pal_futurama()(2)) +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = "top",
		panel.grid.major.x = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9)
	)

>>>>

attrition <- attrition %>% 
	mutate(
		valid_gaze = valid_gaze_prime & valid_gaze_target,
		valid_status = case_when(
			!valid_gaze ~ "Invalid gaze",
			!valid_participant ~ "Invalid participant",
			TRUE ~ "Valid"
		))

participants <- participants %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(participant) %>% 
	left_join(vocabulary) %>% 
	mutate(is_imputed = ifelse(is_imputed, "Imputed", "Observed")) %>% 
	filter(location=="Barcelona")
```

@@

```{r vocabulary_l1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
sample_size <- participants %>% 
	filter(participant %in% fit_l1_4$data$participant) %>% 
	count(age_group, location)

@@

# vocabulary
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	geom_boxplot(
		aes(lp, vocab_size_l1, colour = is_imputed),
		position = position_dodge(width = 1),
		width = 0.25,
		size = 1
	) +
	geom_point(
		aes(lp, vocab_size_l1, color = is_imputed),
		size = 1,
		alpha = 0.75,
		position = position_jitter(width = 0.1, seed = 888)
	) +
	geom_text(
		data = sample_size_lp,
		aes(
			x = 1.5,
			y = 0, 
			label = paste0("N = ", n),
			group = lp
		),
		colour = "black",
		show.legend = FALSE, 
		position = position_dodge(width = 2)
	) +
	labs(
		y = "Receptive vocabulary (L1)", 
		colour = "Imputed", 
		fill = "Imputed",
		title = "L1 vocabulary size",
		subtitle = "Percentage of words in L1 reported to be understood from the vocabulary checklist"
	) +
	scale_color_manual(aesthetics = "slab_color", values = pal_futurama()(2)) +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = "top",
		panel.border = element_rect(fill = NA, colour = "grey", size = 1),
		panel.grid.major.x = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9)
	)

@@

# vocabulary
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	geom_boxplot(
		aes(lp, vocab_size_l1, colour = is_imputed),
		position = position_dodge(width = 1),
		width = 0.25,
		size = 1
	) +
	geom_point(
		aes(lp, vocab_size_l1, color = is_imputed),
		size = 1,
		alpha = 0.75,
		position = position_jitter(width = 0.1, seed = 888)
	) +
	geom_text(
		data = sample_size_lp,
		aes(
			x = 1.5,
			y = 0, 
			label = paste0("N = ", n),
			group = lp
		),
		colour = "black",
		show.legend = FALSE, 
		position = position_dodge(width = 2)
	) +
	labs(
		y = "Receptive vocabulary (total)", colour = "Group", fill = "Group",
		title = "Total vocabulary size",
		subtitle = "Percentage of words in L1+L2 reported to be understood from the vocabulary checklist"
	) +
	scale_color_manual(aesthetics = "slab_color", values = pal_futurama()(2)) +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = "top",
		panel.grid.major.x = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9)
	)

@@

# vocabulary
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
		geom_boxplot(
		aes(lp, vocab_size_l1, colour = is_imputed),
		position = position_dodge(width = 1),
		width = 0.25,
		size = 1
	) +
	geom_point(
		aes(lp, vocab_size_l1, color = is_imputed),
		size = 1,
		alpha = 0.75,
		position = position_jitter(width = 0.1, seed = 888)
	) +
	geom_text(
		data = sample_size_lp,
		aes(
			x = 1.5,
			y = 0, 
			label = paste0("N = ", n),
			group = lp
		),
		colour = "black",
		show.legend = FALSE, 
		position = position_dodge(width = 2)
	) +
	labs(
		y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group",
		title = "Conceptual vocabulary size",
		subtitle = "Percentage of lexicalised concepts reported to be understood from the vocabulary checklist"
	) +
	scale_color_manual(aesthetics = "slab_color", values = pal_futurama()(2)) +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = "top",
		panel.grid.major.x = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9)
	)

### 2022-02-18 docs/05_attrition.Rmd
Render README as target

attrition <- attrition %>% 
	mutate(
		valid_gaze = valid_gaze_prime & valid_gaze_target,
		valid_status = case_when(
			!valid_vocab ~ "Invalid vocabulary",
			!valid_gaze ~ "Invalid gaze",
			!valid_participant ~ "Invalid participant",
			TRUE ~ "Valid"
		))
```

@@

```{r participants_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants, participant, location)) %>% 
	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
	group_by(location, participant, lp, age_group, valid_participant) %>% 
	summarise(
		valid = mean(valid_trial),
		invalid_gaze = mean(!valid_gaze),
		invalid_vocab = mean(!valid_vocab),
		.groups = "drop"
	) %>% 
	relocate(participant) %>% 
	gt() %>% 
	tab_spanner(label = "Invalid trials", columns = starts_with("invalid_")) %>% 
	cols_label(
		participant = "Participant",
		location = "Location",
		lp = "Lang. Profile",
		age_group = "Age",
		valid_participant = "Valid participant",
		valid = "Valid trials (%)",
		invalid_gaze = "Gaze (%)",
		invalid_vocab = "Vocabulary (%)"
	) %>% 
	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab")) %>% 
	as_raw_html()
```

>>>>

attrition <- attrition %>% 
	mutate(
		valid_gaze = valid_gaze_prime & valid_gaze_target,
		valid_status = case_when(
			!valid_gaze ~ "Invalid gaze",
			!valid_participant ~ "Invalid participant",
			TRUE ~ "Valid"
		))
```

@@

```{r participants_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants, participant, location)) %>% 
	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
	group_by(location, participant, lp, age_group, valid_participant) %>% 
	summarise(
		valid = mean(valid_trial),
		invalid_gaze = mean(!valid_gaze),
		.groups = "drop"
	) %>% 
	relocate(participant) %>% 
	gt() %>% 
	tab_spanner(label = "Invalid trials", columns = starts_with("invalid_")) %>% 
	cols_label(
		participant = "Participant",
		location = "Location",
		lp = "Lang. Profile",
		age_group = "Age",
		valid_participant = "Valid participant",
		valid = "Valid trials (%)",
		invalid_gaze = "Gaze (%)"
	) %>% 
	fmt_percent(c("valid", "invalid_gaze")) %>% 
	as_raw_html()
```
